{\steve}: A hierarchical Bayesian model for Supernova Cosmology

### 2019-02-07 papers/methods/paper.tex
Final update hopefully
Ading more text to eqn 4.2.2 for alex

For future use with photometrically classified surveys, we include a simplistic outlier population model. We follow {\rubin} \citep[and therefore ][]{Kunz2007} by implementing a Gaussian mixture model. For surveys with low rates of contamination, it is not possible to fit a contamination population, and the mean of the outlier population has been fixed to the SN~Ia population in prior works. However, with the increased number of contaminants expected in the DES photometric sample, we seek a more physically motivated outlier population.  We find that an acceptable parametrisation is to model the outlier population with a mean absolute magnitude of $\langle M_B^{\rm outl} \rangle = \langle M_B \rangle + \delta_{M_B}^{\rm outl}$, where $\delta_{M_B}^{\rm outl}$ is constrained to be positive, or even to be greater than a small positive number to reduce degeneracy between the two populations.  We note that this represents the mean brightness of outliers, and so outliers could both be brighter and dimmer than the mean SN~Ia absolute magnitude. We set the population width to $\sigma^{\rm outl} = 1$ in $M_B$, $x_1$ and $c$. The probability of each supernova falling into either population is determined by the observed type Ia probability $\hat{p}$ discussed in the previous section. For the spectroscopic survey, we set this to unity. For the photometric proof-of-concept we provide an accurate probability estimate. Further investigation on the effect of inaccurate estimates will be left for future improvements during the analysis of the DES photometric sample.

@@

\begin{align}
&P({\rm data}|\theta) = \notag \\
&\int\, d\mu\, d\eta\, dz \ P( \hat{\eta}, \hat{\mathcal{C}}_\eta^{-1} | \eta, \delta \mathcal{Z}_i, \kappa_0, \kappa_1) P(\hat{z}|z) \notag \\
& P(\eta, \hat{m}, \hat{p} | \langle M_B \rangle, \langle x_1^i \rangle, \langle c^i \rangle, \mu, \delta(0), \delta(\infty), \sigma_{M_B}, \sigma_{x_1}, \sigma_c, \alpha, \beta, z) \notag \\
& P(\mu |z, \Omega_m, w) 
\end{align}

>>>>

For future use with photometrically classified surveys, we include a simplistic outlier population model. We follow {\rubin} \citep[and therefore ][]{Kunz2007} by implementing a Gaussian mixture model. For surveys with low rates of contamination, it is not possible to fit a contamination population, and the mean of the outlier population has been fixed to the SN~Ia population in prior works. However, with the increased number of contaminants expected in the DES photometric sample, we seek a more physically motivated outlier population.  We find that an acceptable parametrisation is to model the outlier population with a mean absolute magnitude of $\langle M_B^{\rm outl} \rangle = \langle M_B \rangle + \delta_{M_B}^{\rm outl}$, where $\delta_{M_B}^{\rm outl}$ is constrained to be positive, or even to be greater than a small positive number to reduce degeneracy between the two populations.  We note that this represents the mean brightness of outliers, and so outliers could both be brighter and dimmer than the mean SN~Ia absolute magnitude. We set the population width to $\sigma^{\rm outl} = 1$ in $M_B$, $x_1$ and $c$. The probability of each supernova falling into either population is determined by the observed type Ia probability $\hat{p}$ discussed in the previous section. \added{Thus our likelihood adapts by having probability $\hat{p}$ to fall into the SN~Ia population as given by equation \eqref{eq:l1} and probability $1 - \hat{p}$ to fall into the outlier population, which is also Gaussian with same mean but unitary covariance.}For the spectroscopic survey, we set this to unity. For the photometric proof-of-concept we provide an accurate probability estimate. Further investigation on the effect of inaccurate estimates will be left for future improvements during the analysis of the DES photometric sample.

@@

\begin{align}
&P({\rm data}|\theta) \propto \notag \\
&\int\, d\mu\, d\eta\, dz \ P( \hat{\eta}, \hat{\mathcal{C}}_\eta^{-1} | \eta, \delta \mathcal{Z}_i, \kappa_0, \kappa_1) P(\hat{z}|z) \notag \\
& P(\eta | \langle M_B \rangle, \langle x_1^i \rangle, \langle c^i \rangle, \mu, \delta(0), \delta(\infty), \sigma_{M_B}, \sigma_{x_1}, \sigma_c, \alpha, \beta, z, \hat{m}, \hat{p}) \notag \\
& P(\mu |z, \Omega_m, w),
\end{align}
where $\hat{m}$ and $\hat{p}$ are found on the right-hand-side of the conditional probability because we take them as exact measurements and not dependent on a prior distribution.
